An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/motiv.tex
better wording

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem an {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry error.
Below is a real-world entry missing error example~\cite{yin11anempirical},
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:

@@

When using the password policy overlay in OpenLDAP, 
users have to first include the related schema.
Leaving out the ``include'' entry, 
which have been left by many users~\cite{yin11anempirical}, 
will cause the failure of this LDAP. 
If this user has \app, she can run \app on such a misconfiguration file,
and \app would return:

>>>>

\para{Example~3: Entry missing errors.} 
Many critical system outages result from the fact that an important
entry was missing in the configuration file. 
We call such a problem an {\em entry missing error}.
In a public misconfiguration dataset~\cite{configdataset},
many MySQL failure reports were caused by
missing entry errors.
Below is a real-world entry missing error example~\cite{yin11anempirical}:
when a user wants to use OpenLDAP to enable her directory access
protocol, she needs to use the password policy overlay. This is usually
done through the following entries in the OpenLDAP configuration file:

@@

When using the password policy overlay in OpenLDAP, 
users have to first include the related schema.
Leaving out the {\tt include} entry, 
which has been left out by many users~\cite{yin11anempirical}, 
will cause failure of this LDAP. 
If this user has \app, she can run \app on such a misconfiguration file,
and \app would return:
